### 2015-02-19 proofs.tex
cleaned up s_02 calculation

We consider $s_{0a}$ for $2 \le a$. We see that $s_{01}$ sends $x_a$ to $-x_a$ and $x_i$ for $i \ne a$ to $x_a-x_1$. We see that $s_{0a}f_1=-x_1^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_1\right)$. %todo

@@

We see that $D_2f_1 = \partial_2f_1-c\frac{f_1-s_{12}f_1}{x_2-x_1} + \dots$. %todo

>>>>

We consider $s_{0a}$ for $2 \le a$. We see that $s_{0a}$ sends $x_a$ to $-x_a$ and $x_i$ for $i \ne a$ to $x_i-x_a$. We see that:

\begin{align*}
s_{0a}f_1&=s_{0a}\left(-x_1^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_1\right)\right)\\
&=s_{0a}\left(-x_1^3+c \left(\sum_{i \ne 1,a} x_1x_i(x_1-x_i)\right)+cx_1x_a(x_1-x_a)+c^2 \left(\sum_{i\ne a}\sum_{j \ne a}x_ix_jx_1\right)+2c^2\left(\sum_{i \ne a} x_ix_ax_1\right)+c^2x_a^2x_1\right)\\
&=-(x_1-x_a)^3+c \left(\sum_{i \ne 1,a} (x_1-x_a)(x_i-x_a)(x_1-x_i)\right)+c(x_1-x_a)(-x_a)(x_1)+\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_i-x_a)(x_j-x_a)(x_1-x_a)\right)+2c^2\left(\sum_{i \ne a} (x_i-x_a)(-x_a)(x_1-x_a)\right)+c^2(-x_a)^2(x_1-x_a)\\\end{align*}\begin{align*}
&=-x_1^3+x_a^3+c \left(\sum_{i \ne 1,a} x_1(x_i-x_a)(x_1-x_i)\right)-c \left(\sum_{i \ne 1,a} x_a(x_a-x_i)(x_i-x_1)\right)+c(x_1-x_a)(-x_a)(x_1)+\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_i-x_a)(x_j-x_a)(x_1-x_a)\right)+2c^2\left(\sum_{i \ne a} (x_i-x_a)(-x_a)(x_1-x_a)\right)+c^2(-x_a)^2(x_1-x_a)\\
&=-x_1^3+x_a^3+c \left(\sum_{i \ne 1,a} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i \ne 1,a} x_ax_i(x_a-x_i)\right)+c\left(\sum_{i \ne 1,a}-x_1^2x_a+x_a^2x_1\right)+c(x_1-x_a)(-x_a)(x_1)+\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_i-x_a)(x_j-x_a)(x_1-x_a)\right)+2c^2\left(\sum_{i \ne a} (x_i-x_a)(-x_a)(x_1-x_a)\right)+c^2(-x_a)^2(x_1-x_a)\\
&=-x_1^3+x_a^3+c \left(\sum_{i \ne 1,a} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i \ne 1,a} x_ax_i(x_a-x_i)\right)
-cx_1x_a(x_1-x_a)+\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_i-x_a)(x_j-x_a)(x_1-x_a)\right)+2c^2\left(\sum_{i \ne a} (x_i-x_a)(-x_a)(x_1-x_a)\right)+c^2(-x_a)^2(x_1-x_a)\\
&=-x_1^3+x_a^3+c \left(\sum_{i \ne 1,a} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i \ne 1,a} x_ax_i(x_a-x_i)\right)
+cx_1x_a(x_1-x_a)-cx_1x_a(x_a-x_1)+\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_i-x_a)(x_j-x_a)(x_1-x_a)\right)+2c^2\left(\sum_{i \ne a} (x_i-x_a)(-x_a)(x_1-x_a)\right)+c^2(-x_a)^2(x_1-x_a)\\
&=-x_1^3+x_a^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)
+\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_i-x_a)(x_j-x_a)(x_1-x_a)\right)+2c^2\left(\sum_{i \ne a} (x_i-x_a)(-x_a)(x_1-x_a)\right)+c^2(-x_a)^2(x_1-x_a)\\
&=-x_1^3+x_a^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)
+\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_ix_j-x_ax_j-x_ax_i+x_a^2)(x_1-x_a)\right)+2c^2\left(\sum_{i \ne a} (x_a^2-x_ax_i)(x_1-x_a)\right)+c^2x_a^2(x_1-x_a)\\
&=-x_1^3+x_a^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)
+\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_ix_j+x_a^2)(x_1-x_a)\right)+c^2\left(\sum_{i \ne a} x_ax_i(x_1-x_a)\right)+c^2\left(\sum_{i \ne a} (x_a^2-x_ax_i)(x_1-x_a)\right)+c^2x_a^2(x_1-x_a)\\
&=-x_1^3+x_a^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)
+\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_ix_j+x_a^2)(x_1-x_a)\right)+c^2\left(\sum_{i \ne a} x_a^2(x_1-x_a)\right)+c^2x_a^2(x_1-x_a)\\\end{align*}\begin{align*}
&=-x_1^3+x_a^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)
+c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_ix_j)(x_1-x_a)\right)+\\&2c^2\left(\sum_{i \ne a} x_a^2(x_1-x_a)\right)+c^2x_a^2(x_1-x_a)\\
&=-x_1^3+x_a^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)
+c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_ix_j)(x_1-x_a)\right)+\\& 2c^2x_a^2(x_1-x_a)+c^2x_a^2(x_1-x_a)\\
&=-x_1^3+x_a^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)
+c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_ix_j)(x_1-x_a)\right)\\
&=-x_1^3+x_a^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)
+c^2 \left(\sum_{i\ne a}\sum_{j \ne a}x_ix_jx_1-x_ix_jx_a)\right)\\
&=f_1-f_a
\end{align*}

Then $\frac{f_1-s_{0a}f_1}{x_a}=-f_a/x_a=x_a^2+c \left(\sum_{i=1}^{n-1} x_i(x_i-x_a)\right)-c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)$.

@@

We see that $D_2f_1 = \partial_2f_1-c\frac{f_1-s_{12}f_1}{x_2-x_1} -c\frac{f_1-s_{02}f_1}{x_2}$.
